
\section{Introduction}
\input{introduction.tex}

% Head 1
\section{State of the art}
\label{StateOfTheArt}
Many researchers have already mentioned some challenges regarding nano data centers. Still, they focus more on the positive aspects of them rather than explaining these challenges. For this reason this paper is focusing on identifying these challenges in more detail. In this section, the state of the art on the current research on nano data centers is presented. 
\input{echos.tex}
\input{nada.tex}
\input{EumEtAl.tex}
% Close with clever questions at the end
\\ \\
As shown, there are several papers explaining the research which has gone into developing nano data center infrastructures. However, even so these papers come to a positive conclusion, no follow up action being taken to turn these theoretical ideas into actual prototypes and systems. Maybe some of the political, legal and technical issues mentioned in these papers require more in depth research?

\section{Challenges towards a distributed Nano Data Center Infrastructure}
\label{sec:challenges}
%includes Interview and confrontation of technical similar systems
In the following sections, the methodology is described, whereafter political, legal and technical challenges are presented.

\subsection{Methodology}
\input{Methodology.tex}

%\subsection{Challenges}

\subsection{Political and legal challenges}
\input{political_challenges.tex}

\subsection{Technical challenges}
\input{energy_consumption.tex}

\section{Evaluation/Results}
\input{evaluation.tex}

\section{Discussion}
\input{discussion.tex}


\section{Conclusion and Future Work}
\input{futurework}


% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

% Appendix
\appendix
\section{Questionnaire}
\input{questionnaire.tex}

