\subsection{ECHOS}
ECHOS introduces a concept for Nano Data Centers that can or should completely replace monolithic data centers \cite{Laoutaris:2008:EEC:1341431.1341442}. The authors call it a radical solution for data management and provision.
According to this concept, so-called "boxes" are set up at the edges of the network, eg. in home gateways (see \cite{technicolor}). These boxes communicate with each other via a peer-to-peer system. The peer-to-peer system as well as the bandwidth is controlled by a central unit, such as the ISP. However, the approach of networking boxes via a peer-to-peer system, and thus providing or sharing content, requires some conditions. So it is first necessary to provide a distributed hosting edge infrastructure. Furthermore, there are also some other problems mentioned. In ECHOS these are listed as follows \cite{Laoutaris:2008:EEC:1341431.1341442}:
\begin{itemize}
	\item "Lack of service guarantees due to uncontrolled interface between different applications."
	\item "Inefficient use of network's and other peer's resources and consequently suboptimal performance."
	\item "Even if sufficient status information is in place, still P2P is inherently unable to use it as it was designed around selfish user behavior and free-riding prevention mechanism [...]."
	\item "Absence of security and control make it impossible to guarantee the integrity and security of content."
\end{itemize}
The problems here are only superficially addressed, and accordingly the solutions to the problems are more general. In this thesis it is conveyed that it is very easy to develop a nano data center platform. The solutions are rather unsatisfactory, and require more investigations.