\begin{enumerate}
\label{appendix:quest}
\item On the website of the LRZ it can be read that \textit{Green IT} is important \cite{LRZGreenIT}. What has been achieved or improved so far?
\item In 2012, the LRZ was awarded the German Data Center Award for \textit{energy and resource efficient data centers} \cite{LRZGreenIT}. What makes the LRZ better on \textit{Green IT} than other data centers?
\item What does the LRZ offer its customers? Are there any special \textit{Green IT} services available? Does the customer have an influence on more environmentally conscious use?
\item Today's use of Internet services has changed massively \cite{TheZetta68:online}. How has the LRZ adapted accordingly?
\item Why are the big data centers still so popular? What are the reasons/advantages? Are these political, economic or technical?
\item Are there any disadvantages with monolithic data centers?
\item Have you heard of an alternative solution to monolithic data centers? There are, among others, some research on nano data centers. Does the LRZ also work with these approaches? What is your opinion?
\item In your opinion, what are the advantages and disadvantages of nano data centers?
\item How does the LRZ see the data centers of the future? What could be possible? Is it realistic that monolithic data centers could be replaced by special peer-to-peer networks?
\item Do you think there are any difficulties or special challenges that need to be solved in order to implement nano data centers suitable for the mass or as new state of the art? What are the difficulties oder challenges in your opinion?
\item Do you have any idea or approach how to solve these difficulties or challenges?
\item Would you have an idea for other alternative systems?
\end{enumerate}