\documentclass[review=true, screen, acmlarge]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
\pagestyle{plain} % remove running headers

\usepackage{booktabs} % For formal tables
\usepackage[utf8]{inputenc} %use utf-8 to enable german (and other non-ascii) character encodings
\usepackage{csquotes} % for quotes / blockquotes


%\usepackage[ruled]{algorithm2e} % For algorithms
%\renewcommand{\algorithmcfname}{ALGORITHM}
%\SetAlFnt{\small}
%\SetAlCapFnt{\small}
%\SetAlCapNameFnt{\small}
%\SetAlCapHSkip{0pt}
%\IncMargin{-\parindent}


% Document starts
\begin{document}
% Title portion
\title{CTNDCI:  Identifying the Political, Legal and Technical Challenges Towards a distributed Nano Data Center Infrastructure} 

\author{Melanie Hauser}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{melanie.hauser@campus.lmu.de}

\author{Diana Irmscher}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{d.irmscher@campus.lmu.de}

\author{Katrin Kolb}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{katrin.kolb@campus.lmu.de}

\author{Mengchu Li} 
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{mengchu.li@yahoo.com}

\author{Katharina Rupp}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{katharina.rupp@web.de}

\author{Andreas Scholz}
\affiliation{%
  \institution{LMU Munich}
  \city{Munich} 
  \country{Germany}}
\email{andreas.scholz@campus.lmu.de}




\begin{abstract}
% One or two sentence fpr basic introduction
With the global increase in IP traffic the question of how to provide and deliver data is becoming increasingly important. Monolithic data centers, as they are used today, pose several problems, such as high energy consumption and lack of scalability.
% two or three sentence for more detailed background
An alternative solution mitigating the problems of monolithic data centers has been proposed in the form of a distributed nano data center infrastructure. Research has shown this to be a superior solution. 
% one sentence about general problem
However, no widespread solution based on a nano data center infrastructure has been implemented as of yet. In this paper we identify the challenges currently preventing nano data centers from becoming the dominant form of content provision on the internet.
By identifying the main challenges nano data centers are facing steps can be taken to overcome these challenges in a more focused way, leading to a more economic data distribution.
% One sentence about main result
Here we show the main challenges for implementing a nano data center platform, categorized in political, legal and technical issues.
% two or three sentence explaining what the main result reveals in direct comparision to what was trought to be the case previously, or how the main result adds to previous knowledge
In this paper, we examined the factors that mainly prevent nano data center from being used. We also found out that nano data centers are not as energy-efficient as they are supposed to be (under certain aspects).
% One or two sentence to put the result into a more general context
For the implementation of a nano data center platform, a number of technical and non-technical aspects are still to be investigated.
%broader perspective




\end{abstract}


\keywords{Green IT; Nano data center; Energy consumption; Security; Availability; Scalability; Data distribution}

\maketitle

\input{body}

\end{document}
